---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(DataExplorer)
```

```{r}
train <- read.csv("../data/train.csv")
test <- read.csv("../data/test.csv")
meta <- read.csv("../data/metadata.csv")
```

```{r}
prep_data <- function(x, test=F){
  for(j in 1:nrow(meta)){
    
    if(str_detect(meta[j, 2], "^Qualitativo")){
      
      if(str_detect(meta[j, 2], "Qualitativo ordinal")){
        x[,j] <- factor(x %>% pull(j), ordered=T)
      }else if(str_detect(meta[j, 2], "Qualitativo nominal")){
        x[,j] <- as.factor(x %>% pull(j))
      }   
    }
  }
  if(test==F){
    x$y = as.factor(x$y)
  }
  
  return(x)
}

train <- prep_data(train)
```

```{r}
num_features <- train %>% select_if(is.numeric) %>% colnames()
cat_features <- train %>% select_if(is.factor) %>% select(-id) %>% colnames()
```

# Análise instrodutória
```{r}
plot_intro(train)
```
Não tem missing explicíto, mas há missing especial
```{r}
missing_999_num <- train %>% select_if(is.numeric) %>% select(where(~any(.==-999))) %>% colnames()
missing_999_num
```

```{r}
missing_999_cat <- train %>% select_if(is.factor) %>% select(where(~any(. == -999))) %>% colnames()
missing_999_cat
```

# Variáveis categóricas
```{r}
plot_bar(train, nrow =2, ncol = 4)
```
id: 14123 categories
var2: 85 categories
var3: 2443 categories
var4: 13094 categories
var5: 6296 categories
var6: 1779 categories
var10: 61 categories
var11: 12384 categories
var12: 5270 categories
var13: 1499 categories
var15: 77 categories
var16: 77 categories
var19: 1201 categories
var21: 1534 categories
var34: 69 categories
var35: 567 categories

```{r}
train %>% group_by(var4) %>% count() %>% arrange(desc(n))
train %>% filter(var4 != -999) %>% 
ggplot(aes(var4, fill = y)) +
  geom_bar()
```
```{r}
train %>% filter(var4 != -999) %>% 
ggplot(aes(factor(y), as.numeric(var4))) +
  geom_boxplot()
```

```{r}
train %>% select_if(is.factor) %>% 
  map_dbl(~length(unique(.x)))

```

# VAriáveis numéricas
```{r}
plot_histogram(train)
```

```{r}
plot_boxplot(train, by = "y")
```

